Case Study: 16S microbiome data (Schubert et al., 2014)

### 2018-06-24 datasets/microbiome/microbiome-enigma.Rmd
Add results plots for mean abunandance covariate

```{r, ph-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(ph_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = ph_bench_file_abun)
} else {
    sb <- readRDS(ph_bench_file_abun)
}
```

@@

```{r, so4-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(so4_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = so4_bench_file_abun)
} else {
    sb <- readRDS(so4_bench_file_abun)
}
```

@@

```{r, al-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(al_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = al_bench_file_abun)
} else {
    sb <- readRDS(al_bench_file_abun)
}
```

@@

```{r, eval = FALSE}
plotMethodRanks(c(so4_bench_file, ph_bench_file, al_bench_file), 
                colLabels = c("SO4", "pH", "Al"), 
                alpha = 0.10, xlab = "Comparison")
```

>>>>

```{r, ph-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(ph_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = ph_bench_file_abun)
} else {
    sb <- readRDS(ph_bench_file_abun)
}
```
### Benchmark Metrics

```{r, ph-metrics-abun, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, ph-plot-abun, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, so4-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(so4_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = so4_bench_file_abun)
} else {
    sb <- readRDS(so4_bench_file_abun)
}
```
### Benchmark Metrics

```{r, so4-metrics-abun, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, so4-plot-abun, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r, al-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(al_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    saveRDS(sb, file = al_bench_file_abun)
} else {
    sb <- readRDS(al_bench_file_abun)
}
```
### Benchmark Metrics

```{r, al-metrics-abun, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, al-plot-abun, width=15, height=15, eval=TRUE}
rejections_scatter( sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r}
plotMethodRanks(c(so4_bench_file, so4_bench_file_abun,
                  ph_bench_file, ph_bench_file_abun,
                  al_bench_file, al_bench_file_abun), 
                colLabels = c("SO4", "SO4-abun", "pH", "ph-abun",
                              "Al", "Al-abun"), 
                alpha = 0.10, xlab = "Comparison")
```

### 2018-06-24 datasets/microbiome/microbiome-goodrich.Rmd
Add results plots for mean abunandance covariate

```{r, goodrich-genus-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ob_goodrich_results.tar.gz"
    saveRDS(sb, file = gns_bench_file_abun)
} else {
    sb <- readRDS(gns_bench_file_abun)
}
```

@@

```{r, eval = FALSE}
plotMethodRanks(c(otu_bench_file, gns_bench_file), 
                colLabels = c("OTU", "Genus"), 
                alpha = 0.10, xlab = "Comparison")
```

>>>>

```{r, goodrich-genus-sb-abun, results="hide", message=FALSE, eval=TRUE}
if (!file.exists(gns_bench_file_abun)) {
    bd <- initializeBenchDesign()
    bd <- dropBMethod(bd, "ashq")
    sb <- buildBench(bd, data = res, ftCols = "ind_covariate")
    metadata(sb)$data_download_link <-
                   "https://zenodo.org/record/840333/files/ob_goodrich_results.tar.gz"
    saveRDS(sb, file = gns_bench_file_abun)
} else {
    sb <- readRDS(gns_bench_file_abun)
}
```
## Benchmark Metrics - mean abun

```{r, goodrich-genus-metrics-abun, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, goodrich-genus-plot-abun, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

```{r, goodrich-genus-overlap-abun}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```

```{r, goodrich-genus-covariates-abun}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```

@@

```{r}
plotMethodRanks(c(otu_bench_file, gns_bench_file, gns_bench_file_abun), 
                colLabels = c("OTU", "Genus", "Genus-abun"), 
                alpha = 0.10, xlab = "Comparison")
```

### 2018-06-24 datasets/microbiome/microbiome-papa.Rmd
Add results plots for mean abunandance covariate

@@

```{r, eval = FALSE}
plotMethodRanks(c(otu_bench_file, gns_bench_file, gns_bench_file_log_ubi), 
                colLabels = c("OTU", "Genus", "Genus - log ubiquity"), 
                alpha = 0.10, xlab = "Comparison")
```

>>>>

## Benchmark Metrics - mean abundance

```{r, papa-genus-abun-metrics, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, papa-genus-abun-plot, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
```

```{r, papa-genus-abun-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots(sb, alpha=0.1, nsets=6, methods=methods)
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

@@

```{r}
plotMethodRanks(c(otu_bench_file, gns_bench_file, 
                  gns_bench_file_log_ubi,gns_bench_file_abun), 
                colLabels = c("OTU", "Genus", "Genus-log", "Genus-abun"), 
                alpha = 0.10, xlab = "Comparison")
```

### 2018-06-24 datasets/microbiome/microbiome-schubert.Rmd
Add results plots for mean abunandance covariate

>>>>

## Benchmark Metrics (mean abun)

```{r, schubert-metrics-abun, eval=TRUE}
assayNames(sb) <- "qvalue"
sb <- addDefaultMetrics(sb)
```

```{r, schubert-plot-abun, width=15, height=15, eval=TRUE}
rejections_scatter(sb, as_fraction=FALSE, supplementary=FALSE)
rejection_scatter_bins(sb, covariate="ind_covariate", supplementary=FALSE)
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
covariateLinePlot(sb, alpha = 0.05, covname = "ind_covariate")
```

# Ubiquity/Abundance comparison

Here we compare the method ranks for the different comparisons at alpha = 0.10.

```{r}
plotMethodRanks(c(otu_bench_file, otu_bench_file_abun), 
                colLabels = c("OTU","OTU-abun"), 
                alpha = 0.10, xlab = "Comparison")
```
